On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-18 Manuscript/manuscript.tex
Fixed carpenter2000bootstrap

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered around the point estimator $\hat\theta_n$ and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

>>>>

\paragraph{Centered Percentile CI}
The procedure for constructing a Centered Percentile CI - referred to as
a Non-Studentized pivotal method - is described in \citet{carpenter2000bootstrap}.
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered around the point estimator $\hat\theta_n$ and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.
